\thornado-hydro: towards discontinuous galerkin methods for supernova hydrodynamics

### 2018-11-24 Documents/Euler/Astronum_2018/ms_endeve.tex
Inclusion of figures in manuscript

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{
  bookmarksnumbered = true,
  bookmarksopen=false,
  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
  pdffitwindow=true,      % window fit to page when opened
  pdfnewwindow=true, % links in new window
  colorlinks=true,           % false: boxed links; true: colored links
  linkcolor=blue,            % color of internal links
  citecolor=magenta,    % color of links to bibliography
  filecolor=magenta,     % color of file links
  urlcolor=cyan              % color of external links
}

@@

@@

@@

>>>>

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx,wrapfig}
\usepackage{hyperref}
\hypersetup{
  bookmarksnumbered = true,
  bookmarksopen=false,
  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
  pdffitwindow=true,      % window fit to page when opened
  pdfnewwindow=true, % links in new window
  colorlinks=true,           % false: boxed links; true: colored links
  linkcolor=blue,            % color of internal links
  citecolor=magenta,    % color of links to bibliography
  filecolor=magenta,     % color of file links
  urlcolor=cyan              % color of external links
}

@@

\subsubsection{Isentropic Vortex}

\begin{wrapfigure}{l}{2.825in}
  \includegraphics[width=18pc]{./Figures/IsentropicVortex_Astronum_2018}
  \caption{\label{fig:IsentropicVortex}Convergence results for the Isentropic Vortex test.}
\end{wrapfigure}

@@

\begin{wrapfigure}{r}{2.825in}
  \includegraphics[width=18pc]{./Figures/KelvinHelmholtz_TCI_24_Astronum_2018}
  \caption{\label{fig:KelvinHelmholtz_TCI}Distribution of elements flagged for limiting in the KH test at $t=2.4$.}
\end{wrapfigure}

@@

\subsubsection{Liska-Wendroff Explosion}

\begin{figure}[h]
  \centering
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/Explosion_Astronum_2018}
  \end{minipage}\hspace{0.5pc}%
  \begin{minipage}{18pc}
    \includegraphics[width=18pc]{./Figures/Explosion_TCI_Astronum_2018}
  \end{minipage}
  \caption{\label{fig:Implosion}Plots for the Liska-Wendroff Explosion problem at $t=3.2$.}
\end{figure}
